---
title: "hw"
output: github_document
---
# load data file
```{r}
load("./nba2017-salary-points.RData")
ls()
```
## A bit of data preprocessing
```{r}
salary_million<-round(salary/1000000,2)
position <- factor(position, levels=c('C','SF','PF','SG','PG'), labels=c( 'center','small_fwd','power_fwd','shoot_guard','point_guard'))
table(position)
```

## Scatterplot of Points and Salary

```{r}
plot(points,salary_million,xlab = 'Points',ylab = 'Salary(in millions)',main = "Scatterplot of Points and Salary",cex=1,pch=19,col='coral')
```

## Correlation between Points and Salary
```{r}
n<-length(points)
cat(sep="", "n=",n,"\n")
mean_points<-sum(points)/n
cat(sep="", "mean_points=",mean_points,"\n")
mean_salary<-sum(salary_million)/n
cat(sep="", "mean_salary=",mean_salary,"\n")
var_points<-sum((points-mean_points)^2)/(n-1)
cat(sep="", "var_points=",var_points,"\n")
var_salary<-sum((salary_million-mean_salary)^2)/(n-1)
cat(sep="", "var_salary=",var_salary,"\n")
sd_points<-sqrt(var_points)
cat(sep="", "sd_points=",sd_points,"\n")
sd_salary<-sqrt(var_salary)
cat(sep="", "sd_salary=",sd_salary,"\n")
cov_xy<-sum((points-mean_points)*(salary_million-mean_salary))/(n-1)
cat(sep="", "cov_xy=",cov_xy,"\n")
cor_xy<-cov_xy/(sd_points*sd_salary)
cat(sep="", "cor_xy=",cor_xy,"\n")
```
## Simple Linear Regression
```{r}
b1<-cor_xy*sd_salary/sd_points
b1
b0<-mean_salary-b1*mean_points
b0
predict_salary<-b1*points+b0
```
###Summary statistics of Y
```{r}
summary(predict_salary)
```
###the regression equation
$Y = 1.509077 + 0.008557567*x$

The slope is positive, the score is positively correlated with the salary,which means that the high score is in exchange for high salary.

when the points equal zero,the intercept which represents salary equals 1.509077.This shows that the basic salary of the NBA player is about $1.509077 million

###the predicted salary for a player that scores
```{r}
cat(sep=" ", " 0   points"," salary=",1.509077 + 0.008557567*0,"\n")
cat(sep=" ", " 100 points"," salary=",1.509077 + 0.008557567*100,"\n")
cat(sep=" ", " 500 points"," salary=",1.509077 + 0.008557567*500,"\n")
cat(sep=" ", "1000 points"," salary=",1.509077 + 0.008557567*1000,"\n")
cat(sep=" ", "2000 points"," salary=",1.509077 + 0.008557567*2000,"\n")
```
##Plotting the regression line
```{r}
plot(points,salary_million,xlab = 'Points',ylab = 'Salary(in millions)',main = "Scatterplot of Points and Salary",cex=1,pch=19)
abline(a=b0,b=b1,col='blue',lwd=3)
lines(lowess(points,salary_million), col ='red',lwd=3)
text(2400, 30,'lowess',col = 'red')
text(2400, 20,'regression',col = 'blue')
```

##Regression residuals and Coefficient of Determination R2
```{r}
residuals<-salary_million-predict_salary
summary(residuals)
```

```{r}
RSS<-sum(residuals^2)
cat(sep="", "RSS=",RSS,"\n")
TSS<-sum((salary_million-mean(salary_million))^2)
cat(sep="", "TSS=",TSS,"\n")
R2<-1-RSS/TSS
cat(sep="", "R2=",R2,"\n")
```
##Exploring Position and Experience
```{r}

```

```{r}

```

```{r}
plotdata<-data.frame(salary_million,position)
boxplot(salary_million~position,data=plotdata,xlab = 'Position',ylab ='Salary(in millions)')
```

Position does not seem to be related with Salary
